---
title: "CSSE COVID19 overview"
author: "Niek Den Teuling"
date: "2020-10-23"
editor_options: 
  chunk_output_type: inline
params:
  minDate: 2020-03-01
  maxDate: 2022-01-01
---

```{r setup, include=FALSE}
minDate = as.Date(params$minDate)
maxDate = as.Date(params$maxDate)
knitr::opts_chunk$set(echo = TRUE)
```

# Data
```{r}
alldata = load_csse_covid19_data()

data = alldata %>%
  .[Date %between% c(minDate, maxDate)] %>%
  .[Population > 0]
```

* `r uniqueN(alldata$State)` states.
* `r uniqueN(alldata$Combined_Key) %>% comma()` counties.
* `r uniqueN(alldata$Date)` observation days (`r min(alldata$Date)` to `r max(alldata$Date)`).

```{r warning=FALSE}
countyTable = alldata[, .(
  ObservationDays = uniqueN(Date),
  InfectionStart = first(Date[Confirmed > 0]),
  Population = max(Population*1),
  Confirmed = max(Confirmed)
  ), 
  keyby = .(State, County)]

stateTable = countyTable[, .(
  Counties = .N,
  ObservationDays = max(ObservationDays),
  InfectionStart = min(InfectionStart, na.rm=TRUE),
  Population = sum(Population),
  Confirmed = sum(Confirmed)
), keyby = State]
```

# Nation-wide
```{r}
nationData = data[, .(
  Confirmed = sum(Confirmed)
  ), 
  keyby=Date] %>%
  .[, Confirmed7 := movmeanc(Confirmed, 7)] %>%
  .[, NewConfirmed := c(0, diff(Confirmed))] %>%
  .[, NewConfirmedWeekly := movsumr(NewConfirmed, 7) / 7] %>% # identical to 3-day shifted diff(Confirmed7)
  .[, NewConfirmed7 := c(0, diff(Confirmed7))]
```

## Cumulative cases
```{r}
ggplot(nationData, aes(x = Date, y = Confirmed)) +
  scale_y_continuous(breaks = pretty_breaks(10), labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line(size = 1) +
  geom_line(aes(y = Confirmed7), color = 'red') +
  labs(title = 'Cumulative cases nation-wide')
```

```{r}
ggplot(nationData, aes(x = Date, y = Confirmed)) +
  scale_y_log10(labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line(size = 1) +
  geom_line(aes(y = Confirmed7), color = 'red') +
  labs(title = 'Cumulative cases nation-wide')
```

## New cases
```{r}
ggplot(nationData, aes(x = Date, y = NewConfirmed)) +
  scale_y_continuous(breaks = pretty_breaks(10), labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line(size = 1) +
  geom_line(aes(y = NewConfirmed7), color='red') +
  labs(title = 'New cases nation-wide')
```

```{r}
alldata[, .(NormNewConfirmed = mean(NormNewConfirmed, na.rm=TRUE)), by=DayOfWeek] %>%
  ggplot(aes(x = DayOfWeek, y = NormNewConfirmed)) +
  geom_bar(stat = 'identity')
```

```{r}
alldata[, .(NewCaseReports = sum(NewConfirmed > 0, na.rm=TRUE)), by=DayOfWeek] %>%
  ggplot(aes(x = DayOfWeek, y = NewCaseReports)) +
  scale_y_continuous(labels = comma) +
  geom_bar(stat = 'identity')
```


# State-level
`r stateTable[order(-Counties)] %>% .[, Population := comma(Population)] %>% .[, Confirmed := comma(Confirmed)] %>% DT::datatable()`

```{r}
stateData = data %>%
  .[, .(Confirmed = sum(Confirmed), Population = sum(Population)), keyby=.(State, Date)] %>%
  .[, Confirmed7 := movmeanc(Confirmed, 7), by=State] %>%
  .[, NewConfirmed := c(0, diff(Confirmed)), by=State] %>%
  .[, NewConfirmed7 := c(0, diff(Confirmed7)), by=State]
```

## Cumulative cases
```{r}
ggplot(stateData, aes(x = Date, y = Confirmed, group = State)) +
  scale_y_continuous(breaks = pretty_breaks(10), labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line() +
  labs(title = 'Cumulative cases state-wide')
```
## New cases
```{r}
ggplot(stateData, aes(x = Date, y = NewConfirmed, group = State)) +
  scale_y_continuous(breaks = pretty_breaks(10), labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line(size = 1) +
  geom_line(aes(y = NewConfirmed7), color='red', alpha = .5) +
  labs(title = 'New cases state-wide')
```

```{r}
ggplot(stateData, aes(x = Date, y = NewConfirmed / Population * 1e5, group = State)) +
  scale_y_continuous(breaks = pretty_breaks(10), labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  coord_cartesian(ylim=c(0, 100)) +
  geom_line(size = 1) +
  geom_line(aes(y = NewConfirmed7 / Population * 1e5), color='red', alpha=.5) +
  labs(title = 'Normalized new cases state-wide', subtitle = 'Trimmed to 100 cases / 1e5')
```

```{r warning=FALSE}
ggplot(stateData, aes(x = Date, y = NewConfirmed / Population * 1e5 + .01, group = State)) +
  scale_y_log10(labels=comma) +
  scale_x_date(breaks = pretty_breaks(10)) +
  geom_line() +
  geom_line(aes(y = NewConfirmed7 / Population * 1e5 + .01), color='red', alpha=.5) +
  labs(title = 'Normalized new cases state-wide')
```

# County-level
```{r}
countyData = data %>%
  .[, Confirmed7 := movmeanc(Confirmed, 7), by=.(State, County)] %>%
  .[, NewConfirmed := c(0, diff(Confirmed)), by=.(State, County)] %>%
  .[, NewConfirmed7 := c(0, diff(Confirmed7)), by=.(State, County)]
```

## Cumulative cases {.tabset .tabset-pills}
```{r warning=FALSE, results='asis'}
states = unique(data$State) %>% as.character()
for (state in states) {
    cat('###', state, '<br>', '\n')
    
    plot.new()
    print(ggplot(countyData[State == state], aes(x = Date, y = Confirmed + .1, group = County)) +
        scale_y_log10() +
        scale_x_date(breaks = pretty_breaks(10)) +
        geom_line() +
        geom_line(aes(y = Confirmed7 + .1), color = 'red', alpha = .5) +
        labs(title='Confirmed cases', subtitle = state))
    
    dev.off()
    plot.new()
    dev.off()
}
```
## New cases {.tabset .tabset-pills}
```{r warning=FALSE, results='asis'}
states = unique(data$State) %>% as.character()
for (state in states) {
    cat('###', state, '<br>', '\n')
    
    plot.new()
    print(ggplot(countyData[State == state], aes(x = Date, y = NewConfirmed + .1, group = County)) +
        scale_y_log10() +
        scale_x_date(breaks = pretty_breaks(10)) +
        geom_line() +
        geom_line(aes(y = NewConfirmed7 + .1), color = 'red', alpha = .5) +
        labs(title='New confirmed cases', subtitle = state))
    
    dev.off()
    plot.new()
    dev.off()
}
```

## Normalized new cases {.tabset .tabset-pills}
```{r warning=FALSE, results='asis'}
states = unique(data$State) %>% as.character()
for (state in states) {
    cat('###', state, '<br>', '\n')
    
    plot.new()
    print(ggplot(countyData[State == state], aes(x = Date, y = NewConfirmed / Population * 1e5 + .1, group = County)) +
        scale_y_log10() +
        scale_x_date(breaks = pretty_breaks(10)) +
        geom_line() +
        geom_line(aes(y = NewConfirmed7 / Population * 1e5 + .1), color = 'red', alpha = .5) +
        labs(title='New confirmed cases', subtitle = state))
    
    dev.off()
    plot.new()
    dev.off()
}
```

# Session info
```{r}
sessionInfo()
```

