---
title: "Analysis of class enumeration simulation study"
author: "Niek Den Teuling"
date: "2022-02-08"
params:
  experiment: class_gmmrmv_final2
  simFields: model, data.numGroups, data.fixed, data.random, data.randomSigma, data.cv, data.seed
  clusterFields: nClusters, AlphaCor, ConvProp, AllConverged, thetaMin
  metricFields: LogLik, mWAIC, p_waic1, p_waic2, BIC
  metric: mWAIC
output:
  html_document: 
    toc: yes
    highlight: tango
    number_sections: yes
---

# Preparation
```{r setup, results='hide'}
suppressPackageStartupMessages({
  library(effectsize)
  library(emmeans)
  library(multcomp)
})

allSimFields = stringr::str_split(params$simFields, ',\\s*')[[1]]
allClusterFields = stringr::str_split(params$clusterFields, ',\\s*')[[1]]
allMetricFields = stringr::str_split(params$metricFields, ',\\s*')[[1]]
datasimConds = setdiff(allSimFields, 'seed')
metric = params$metric
```

```{r, results='hide'}
expFile = file.path(RESULTS_DIR, paste0(params$experiment, '.rds'))
dtAllModels = readRDS(expFile) %>%
  as.data.table() %>%
  .[, AllConverged := is.finite(ConvProp) & ConvProp == 1] %>%
  .[]
assert_that(
  noNA(dtAllModels$ConvProp), 
  msg = 'One or more model evaluations have NaN ConvProp value, indicating a parameter processing issue'
)

simFields = intersect(allSimFields, names(dtAllModels))
clusterFields = intersect(allClusterFields, names(dtAllModels))
metricFields = intersect(allMetricFields, names(dtAllModels))

assert_that(hasName(dtAllModels, metric))

dtModels = dtAllModels %>%
  subset(select = unique(c(simFields, clusterFields, metricFields))) %>%
  .[, i := .GRP, keyby = simFields] %>%
  .[, data.i := .GRP, keyby = datasimConds]
nClusterOptions = unique(dtModels$nClusters)

message(uniqueN(dtModels$i), ' unique data scenarios')
```

Determine valid models.
```{r}
dtValidModels = dtModels[abs(AlphaCor) < .9]
message(
  sprintf(
    'Dropped %d/%d invalid models (%g%%)', 
    nrow(dtModels) - nrow(dtValidModels),
    nrow(dtModels),
    (nrow(dtModels) - nrow(dtValidModels)) / nrow(dtValidModels) * 100
  )
)

validSims = dtValidModels[, all(nClusterOptions %in% nClusters), keyby = i] %>%
  .[V1 == TRUE, .(i)]

dtValidSimModels = dtValidModels[validSims, on = 'i']
setkeyv(dtValidSimModels, c(datasimConds, 'AllConverged', metric))
assert_that(nrow(dtValidSimModels) > 0)

message('Valid simulation scenarios: ', nrow(validSims) / uniqueN(dtValidModels$i) * 100, '%')
```

# Results for all models
```{r}
# select the preferred model per nClusters setting in case of multiple runs through seed argument.
dtValidSimModelsBest = dtValidSimModels[
  order(-AllConverged, mWAIC), 
  first(.SD), 
  keyby = .(i, nClusters)
]

assert_that(
  dtValidSimModelsBest[, 
    .N == length(nClusterOptions) && setequal(nClusters, nClusterOptions), 
    keyby = .(i)
  ][, all(V1)],
  msg = 'Implementation error: some simulation conditions have more than 1 model per nClusters setting'
)

dtValidWide = dcast(
  dtValidSimModelsBest, 
  model + data.fixed + data.random + data.randomSigma + data.cv + data.seed ~ paste0('K', nClusters),
  value.var = metric
)
```

## Convergence rate
Compute complete convergence per model.
```{r}
dtValidSimModels[, .(
  Converged = mean(AllConverged, na.rm = TRUE)
), keyby = .(data.fixed, data.cv, data.randomSigma, model, nClusters)]
```

## mLogLik
```{r}
ggplot(dtValidSimModelsBest, aes(x = nClusters, y = LogLik, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + data.cv + data.randomSigma + model)
```

## mWAIC
```{r}
ggplot(dtValidSimModelsBest, aes(x = nClusters, y = mWAIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + data.cv + data.randomSigma + model, scales = 'free_y')
```

## p_waic
```{r}
ggplot(dtValidSimModelsBest, aes(x = nClusters, y = p_waic1, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model, scales = 'free_y')

ggplot(dtValidSimModelsBest, aes(x = nClusters, y = p_waic2, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model, scales = 'free_y')
```

## BIC
```{r}
ggplot(dtValidSimModels, aes(x = nClusters, y = BIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model, scales = 'free_y')
```

## Solo-run class recovery
```{r}
dtValidWide[, 
  Kmin := apply(as.matrix(.SD), 1, which.min), 
  .SDcols = paste0('K', 1:3), 
  keyby = model
]

dtValidWide[, .(
  .N, 
  MinusProp = mean(Kmin == 1), 
  CorrectProp = mean(Kmin == 2), 
  PlusProp = mean(Kmin == 3)), 
  keyby = .(data.fixed, data.cv, data.randomSigma, model)
]
```

## Dataset-averaged class recovery
```{r}
dtMeanValidSims = dtValidSimModels[, .(
  Metric = mean(mWAIC, na.rm = TRUE), 
  Models = .N
), keyby = c('nClusters', datasimConds)]
```

```{r}
dtMeanValidWide = dcast(
  dtMeanValidSims, 
  model + data.fixed + data.randomSigma + data.cv + data.seed ~ paste0('K', nClusters), 
  value.var = c('Metric', 'Models')
)

msg = validate_that(
  noNA(dtMeanValidWide$Metric_K1),
  noNA(dtMeanValidWide$Metric_K2),
  noNA(dtMeanValidWide$Metric_K3)
)
if (!isTRUE(msg)) {
  warning(msg)
}

dtMeanValidWide[, Kmin := apply(as.matrix(.SD), 1, which.min), .SDcols = paste0('Metric_K', 1:3), keyby = model]

dtMeanValidWide[, .(Datasets = .N, MinusProp = mean(Kmin == 1), CorrectProp = mean(Kmin == 2), PlusProp = mean(Kmin == 3)), keyby = .(data.fixed, data.cv, data.randomSigma, model)]
```

# Results for fully converged models
```{r}
convSims = dtValidSimModels[
  AllConverged == TRUE, 
  all(nClusterOptions %in% nClusters), 
  keyby = i
] %>% 
  .[V1 == TRUE, .(i)]

message('Complete scenarios with converged models: ', nrow(convSims) / uniqueN(dtSimModels$i) * 100, '%')

dtConvSimModels = dtValidSimModels[AllConverged == TRUE][convSims, on = 'i']
assert_that(
  nrow(dtConvSimModels) > 0,
  all(dtConvSimModels$AllConverged)
)

dtConvSimModelsBest = dtConvSimModels[
  order(mWAIC), 
  first(.SD), 
  keyby = .(i, nClusters)
]

dtConvWide = dcast(
  dtConvSimModelsBest, 
  model + data.fixed + data.random + data.randomSigma + data.cv + data.seed ~ paste0('K', nClusters),
  value.var = metric
)
```

## mLogLik
```{r}
ggplot(dtConvSimModelsBest, aes(x = nClusters, y = LogLik, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + data.randomSigma + model)
```

## mWAIC
```{r}
ggplot(dtConvSimModelsBest, aes(x = nClusters, y = mWAIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + data.cv + data.randomSigma + model, scales = 'free_y')
```

## p_waic
```{r}
ggplot(dtConvSimModelsBest, aes(x = nClusters, y = p_waic1, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model + data.cv + data.randomSigma, scales = 'free_y')

ggplot(dtConvSimModelsBest, aes(x = nClusters, y = p_waic2, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model + data.cv + data.randomSigma, scales = 'free_y')
```

## BIC
```{r}
ggplot(dtConvSimModelsBest, aes(x = nClusters, y = BIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model + data.cv + data.randomSigma, scales = 'free_y')
```

## Solo-run class recovery
```{r}
dtConvWide[, 
  Kmin := apply(as.matrix(.SD), 1, which.min), 
  .SDcols = paste0('K', 1:3), 
  keyby = model
]

dtConvWide[, .(
  .N, 
  MinusProp = mean(Kmin == 1), 
  CorrectProp = mean(Kmin == 2), 
  PlusProp = mean(Kmin == 3)), 
  keyby = .(data.fixed, data.cv, data.randomSigma, model)
]
```

## Dataset-averaged class recovery
```{r}
dtMeanConvSims = dtConvSimModels[, .(
  Metric = min(mWAIC, na.rm = TRUE), 
  Models = .N
), keyby = c('nClusters', datasimConds)]
```

```{r}
dtMeanConvWide = dcast(
  dtMeanConvSims, 
  model + data.fixed + data.randomSigma + data.cv + data.seed ~ paste0('K', nClusters),
  value.var = c('Metric', 'Models')
)

msg = validate_that(
  noNA(dtMeanConvWide$Metric_K1),
  noNA(dtMeanConvWide$Metric_K2),
  noNA(dtMeanConvWide$Metric_K3)
)
if (!isTRUE(msg)) {
  warning(msg)
}

dtMeanConvWide[, Kmin := apply(as.matrix(.SD), 1, which.min), .SDcols = paste0('Metric_K', 1:3), keyby = model]

dtMeanConvWide[, .(Datasets = .N, MinusProp = mean(Kmin == 1), CorrectProp = mean(Kmin == 2), PlusProp = mean(Kmin == 3)), keyby = .(data.fixed, data.cv, data.randomSigma, model)]
```

# Extra results
## mWAIC per dataset
```{r}
ggplot(dtConvSimModels[data.fixed == 'PartialLinear' & AlphaCor < .9], aes(x = nClusters, y = mWAIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.seed) +
  labs(title = 'PartialLinear')

ggplot(dtConvSimModels[data.fixed == 'EqualLinear'], aes(x = nClusters, y = mWAIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.seed) +
  labs(title = 'EqualLinear')
```

## Shape
```{r}
ggplot(dtConvSimModels[, .(nClusters = nClusters, mWAIC = mWAIC - mean(mWAIC)), keyby=.(data.fixed, model, i)], aes(x = nClusters, y = mWAIC, group = i)) +
  geom_line(size=.1) +
  facet_wrap(~data.fixed + model)
```

## Averaged mWAIC per dataset
```{r}
ggplot(dtMeanConvSims, aes(x = nClusters, y = Metric, group = data.seed)) + geom_line() +
  facet_wrap(~ data.fixed + data.randomSigma + data.cv)
```



